My title

### 2024-10-13 paper/paper.qmd
initial framework & download raw data

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Yunkyung Ko
  - Chenika Bukes
thanks: "Code and data are available at: [https://github.com/koyunkyung/spotify-API](https://github.com/koyunkyung/spotify-API)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(spotifyr)
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Yunkyung Ko
thanks: "Code and data are available at: [https://github.com/koyunkyung/us_election_2024](https://github.com/koyunkyung/us_election_2024)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
```
